---
output: rmarkdown::github_document
---

# tiobeindexr

[![Build Status](https://travis-ci.org/amrrs/tiobeindexr.svg?branch=master)](https://travis-ci.org/amrrs/tiobeindexr) 

## Description

Get latest TIOBE Index Tables. The TIOBE Programming Community index is an indicator of the popularity of programming languages from <https://www.tiobe.com/tiobe-index/>

## Overview

This R package includes the following functions:

* `top_20()`
* `top_50()`
* `long_term_history()`
* `hall_of_fame()`

## Installation

```{r eval=FALSE}
devtools::install_github("amrrs/tiobieindexr")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(tiobieindexr)

# current verison
packageVersion("tiobieindexr")

```

### Extract Top 20 Programming Languages

```{r}
top_20()
```

### Extract Top 50 Programming Languages

```{r}
tail(top_50())
```

### Get Long Term History Programming Index Table

```{r}
long_term_history()
```

### Get Hall of Fame Table

```{r}
hall_of_fame()
```


## Courtesy

The data available in the package is programmatically extracted from 
[TIOBE Index](https://www.tiobe.com/tiobe-index/)
